Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
First half of discussion

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via GLM $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
in one participant.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalize to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired participants.

% PPA: intro
First, we analyzed data from the movie offering ecologically more valid visual
stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
\todo{clusters are pretty big too}
%
Contrary to \citep{bartels2004mapping} who annotated the content of movie
frames, we categorized each frame after a cut independent of its specific
content
% exploited cinematographic tendencies
exploiting a cinematographic confound in the stimulus structure (cf. section
\ref{rationale}):
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that confounding variables would
average out, and our whole-brain analyses would lead to significant clusters in
the PPA.
% results
Group results of the movie stimulus' primary contrast yielded one cluster that
spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features.
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas in individual participants should extensively annotate the
content of frames (e.g.  using the open-source solution ``Pliers'' for feature
extraction from a visual naturalistic stimulus; \citep{mcnamara2017developing}).
% we took advantage of cinematography
We here took advantage of an idiosyncrasy of movie directing to shift from
depicting the spatial layout to to later depicting persons and objects.
% know your stimulus
Given that this shift is common in movies, investigators should be aware that
cinematographic tendencies are part of movie's confound structure that might,
depending on the research question, influence the results.
% conclusion
In summary, results from the visual localizer paradigm using blocks of pictures
generalize to an ad hoc approach to operationalize the perception of spatial
information at the moment of cuts in an audio-visual movie.

% intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we hypothesized that semantic spatial
information embedded in the audio-description stimulus would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\citep{aziz2008modulation} modeled events from on- to offset of sentences
(describing unknown and famous places and faces), and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Study results revealed significantly decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places compared
to famous faces.
% we: model & whole brain
Here we modeled events from on- to offset of single words and performed a
whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

% previous studies: no task
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep participants attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but still: we are different
Our paradigm still differs from \citep{epstein1998ppa} because the modeled
stimulus features were incidentally embedded in a continuous stream of auditory
information preventing participants from making assumptions about the
investigated perceptual process.
% concluding statement: kinda automatic process
Hence, current results also suggest that verbal spatial information is processed
in the anterior PPA casually and does not necessarily rely on deliberately
paying attention to verbal spatial information.

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}).
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        (gray).
        Black: outline of overlapping individual PPA ROIs.
        Light gray: The audio-description's field-of-view (cf.
        \citep{hanke2014audiomovie}).
        The figure shows that some contrasts yielded significant clusters
        also in the lateral temporal and prefrontal cortex.
        }
    \label{fig:stability-slices}
\end{figure*}

@@

\end{document}
\documentclass[english]{article}

>>>>

% previous studies
Several studies have reported increased hemodynamic activity in the PPA,
attributed to the processing of spatial information, for example, when
participants were watching static pictures of landscapes compared to pictures of
faces or objects \citep[e.g.,][]{epstein1998ppa, epstein1999parahippocampal}.
However, reports regarding the correlates of processing spatial information in
non-visual stimulation are less clear \citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we investigated the hemodynamic response to
spatial information using a model-based, mass-univariate approach.
% current study: dissimilar
However, instead of using a conventional set of stimuli, assembled to
specifically and predominantly evoke the processing spatial information, we
employed a naturalistic movie stimulus that was designed for entertainment.

% PPA: intro
In an earlier study, \cite{bartels2004mapping} manually annotated the content
of individual movie frames (color, faces, language, and human bodies) and found
that the expected specialization of functional areas is preserved during movie
watching.
%
In contrast, we aimed to exploit a cinematographic confound in the stimulus
structure, where
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the spatial layout of locations in earlier
shots and only later focus more on detailed depictions of people and objects
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
We hypothesized that due to the complex nature of a naturalistic stimulus,
unrelated factors would be balanced across a large number of events, and make
the bias of spatial information availability in particular events accessible to
convential model-based statistical analysis of BOLD fMRI data.
%
This approach required a detailed description of the occurence of relevant
stimulus features. For both types of naturalistic stimuli used here, a movie
and its audio-description, this annotation revealed the respective number of
incidentally occurring events to be similar to those of a conventional
experimental paradigm used in neuroimaging, for the purpose of localizing
particular regions of interest.

% group AV
On a group-average level, results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
conventionally localized PPA, but also extending into earlier visual cortices.
% group AD
Likewise, results for the audio-description identify significant activation in the PPA
but restricted to its anterior part.
% individual level
Moroever, the group averages are representative for the majority of individual
results, where, for example, the audio-description stimulus yields
bilateral clusters in the anterior PPA of nine participants and a unilateral cluster
in one participant.
% meaning: generalization to naturalistic stimuli
These findings suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie or a purely auditory narrative.
% narrative as substitute
The presented evidence on the in-principle suitability of an auditory-only paradigm
for localizing the PPA, may offer a path to the development of diagnostic procedures
more suitable for populations of individuals with visual impairments or conditions
like nystagmus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.\todo{what is the other evidence?}

% results
Group results of the movie stimulus' primary contrast yielded a large cluster
that spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, earlier visual areas could be
attributed to the temporal averaging across events that did not control for
confounding visual features.
% solution
Future studies that aim to use a movie to localize visual areas in individual
participants should extensively annotate the content of frames \citep[e.g., using the
open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus;][]{mcnamara2017developing}.

% MIH: second time this notion is coming up in the discussion
%% we took advantage of cinematography
%We here took advantage of an idiosyncrasy of movie directing to shift from
%depicting the spatial layout to to later depicting persons and objects.
%% know your stimulus
%Given that this shift is common in movies, investigators should be aware that
%cinematographic tendencies are part of movie's confound structure that might,
%depending on the research question, influence the results.
%% conclusion
%In summary, results from the visual localizer paradigm using blocks of pictures
%generalize to an ad hoc approach to operationalize the perception of spatial
%information at the moment of cuts in an audio-visual movie.

% hypothesis
Based on the report by \cite{aziz2008modulation}, we hypothesized that semantic spatial
information embedded in the audio-description stimulus would correlate with
increased hemodynamic activity in the PPA.
% diff to Aziz (2008)
\cite{aziz2008modulation} modeled events from onset to offset of sentences,
describing unknown and famous places and faces, and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Their results showed decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places in contrast
to famous faces.
% we: model & whole brain
In this study, we modeled events from onset to offset of single words and performed a
voxelwise whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \cite{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

% previous studies: no task
It is common for conventional localizer paradigms to
employ a task to keep participants attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
The naturalistic stimulation paradigm employed here is similar in the sense that participants had no behavioral or
cognitive task \cite[e.g., forming a mental image of the stimuli;][]{ocraven2000mental} but just had to ``enjoy the presentation''.
% but still: we are different
This naturalistic paradigm nevertheless differs from \cite{epstein1998ppa},
because the relevant stimulus features were embedded in a continuous stream of complex
auditory (and visual) information that makes it unlikely that participants
speculate on the purpose of the investigation or perform undesired and unknown
evaluation or categorization of isolated stimuli.
% concluding statement: kinda automatic process
Our results therefore indicate that verbally communicated spatial information
is processed, in the anterior PPA, automatically and without specifically
guided attention.

@@

\begin{figure*}[tbp]
\centering
    \includegraphics[width=\linewidth]{figures/stability-slices}
    \caption{Overlap of significant clusters ($Z$>3.4; $p$<.05, cluster corrected)
        The audio-description's contrasts 1-8 (blue; \ref{tab:ao-contrasts})
        are overlaid over the audio-visual movie's contrasts 1-5 (red;
        \ref{tab:av-contrasts}).
        Cluster are overlaid on top of the MNI152 T1-weighted head template
        with the acquisition field-of-view for the audio-description study
        highlighted.
        Black: outline of overlapping individual PPA ROIs.
        The figure shows that some contrasts yielded significant clusters
        also in the lateral temporal and prefrontal cortex.
        }
    \label{fig:stability-slices}
\end{figure*}

@@

\end{document}
